---
title: "Lab 4"
author: 'Name - here'
output: word_document
---

## Lab Overview

The entire lab will be worth 20 points. 


### 1. R Style (5 points)
The code and output below are designed to summarize a dataset about the titanic. Update the code and output to meet the style guide and make the results reproducible.

Please include a bullet point summary of what you changed and why. 

```{r}
THEDATA=read.csv('http://math.montana.edu/ahoegh/teaching/stat408/datasets/titanic.csv')

library(dplyr)
filter(tally(group_by(select(filter(THEDATA, Survived==1,),Pclass,Sex),Pclass,Sex)), !Pclass %in% c(1,3))

```


There were 70 second class female passengers that survived and  17 male second class passengers that survived and a total of 90 second class passengers that survived.


### 2. Debugging Example (10 points)

The goal of this code is to create a figure of age by passenger class. There are a few bugs in the code, identify and fix them. List all the things that you changed.

```{r}
titanic == read_csv('http://math.montana.edu/ahoegh/teaching/stat408/datasets/titanic.csv')

titanic 
  %>% filter(!is.na(Age)) %>% # removed passengers without age
  mutate(Pclass = factor(Pclass)) %>% # changed class to factor
  ggplot(y = Age, x = Pclass)) %>%
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(color = Sex) +
  theme_bw() + 
  xlab(Passenger Class) +
  ggtitle('Passenger age by class and gender on Titanic')
```


### 3. Data Structures / Subsetting (5 points)

### a. 
How old is the 747th passenger in the dataset?

### b. 
How old is the oldest passenger in the dataset?

### c.

Who is the oldest passenger in the dataset?


### d. 
What percentage of 3rd class males survived (Leonardo DiCaprio as Jack)?


### e. 
What percentage of 1st class females survived (Kate Winslet as Rose).
