---
title: "Lab 4"
format: pdf
editor: source
---

## Lab Overview
For this question, we will explore a few datasets and conduct an exploratory data analysis.

```{r, message = F}
library(tidyverse)
```

### 1. (2 points)

Explore the Capital Bike Share dataset and pose a research question. See data information here: [https://www.kaggle.com/datasets/contactprad/bike-share-daily-data](https://www.kaggle.com/datasets/contactprad/bike-share-daily-data)

```{r}
bikes <- read_csv('https://raw.githubusercontent.com/stat408/Lab4/master/CapitalBikeshare.csv')
```

### 2. (2 points)

Explore the squirrel dataset and pose a research question. See data dictionary here: [https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-10-29](https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-10-29)

```{r}
nyc_squirrels <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-10-29/nyc_squirrels.csv")
```

### 3. (2 points)

Explore the bachelor dataset and pose a research question. See data information here: [https://data.world/aerispaha/the-bachelor-contestants](https://data.world/aerispaha/the-bachelor-contestants)

```{r}
bachelor <- read_csv('https://raw.githubusercontent.com/stat408/Lab4/master/historical_bachelor_contestants.csv')
```

### 4. (14 points)

Select one of the datasets and create at least one figure to address the research question posed for that dataset.

